Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-09-25 draftfinalreport_v4.Rnw
adds cost-benefit table reading, tex + discussion

change<-read.csv("change.csv",header=T)
costtable1<-read.csv("costtable1.csv",header=T)
costtable2<-read.csv("costtable2v2.csv",header=T)
costtable3<-read.csv("costtable3.csv",header=T)
costtable4<-read.csv("costtable4v2.csv",header=T)
costtable5<-read.csv("costtable5v2.csv",header=T)
costtable20<-read.csv("tables/cost_benefit_20.csv",header=T)
costtable50<-read.csv("tables/cost_benefit_50.csv",header=T)
costtable74<-read.csv("tables/cost_benefit_74.csv",header=T)
costtable20_no<-read.csv("tables/cost_benefit_no_20.csv",header=T)
costtable50_no<-read.csv("tables/cost_benefit_no_50.csv",header=T)

@@

@@

>>>>

change<-read.csv("change.csv",header=T)
costtable1<-read.csv("costtable1.csv",header=T)
costtable2<-read.csv("costtable2v2.csv",header=T)
costtable3<-read.csv("costtable3.csv",header=T)
costtable4<-read.csv("costtable4v2.csv",header=T)
costtable5<-read.csv("costtable5v2.csv",header=T)
costtable20<-read.csv("tables/cost_benefit_20.csv",header=T)
costtable50<-read.csv("tables/cost_benefit_50.csv",header=T)
costtable74<-read.csv("tables/cost_benefit_74.csv",header=T)
costtable20_no<-read.csv("tables/cost_benefit_no_20.csv",header=T)
costtable50_no<-read.csv("tables/cost_benefit_no_50.csv",header=T)
costtable_50pc<-read.csv("tables/cost_benefit_50pc.csv",header=T)

@@

\begin{sidewaystable}\footnotesize
<<results=tex,echo=FALSE>>=
colnames(costtable_50pc)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV")
costtable_50pc[,c(2:10,12)] <- round(costtable_50pc[,c(2:10,12)])
costtable_50pc[,11] <- round(costtable_50pc[,11],2)
latex(costtable_50pc, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with \$35.74 dollars per immunised person assuming the cases prevented through additional vaccination each year are equal to the mean annual number of cases per DHB since 2009 (see \autoref{table:vacp}). This is the break-even cost per immunised person (B/C = 1) nationally if 50\% of the currently na\"{\i}ve population were vaccinated. \textit{Vacc} is numbers to immunise if 50\% of the currently na\"{\i}ve population were vaccinated (see \autoref{table:vacp}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}  is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio; \textit{NPV} is the net present value, defined as the sum of the present values of costs and benefits of the vaccination programme.}
\label{table:cost50pc}
\end{sidewaystable}

@@

The last benefit--cost analysis scenario were performed was one in which more than the minimum proportion of na\"{\i}ve were immunised. In this scenario we did not use the \Sexpr{vacc_reqd_percent}\% of currently na\"{\i}ve population necessary to reach adequate national immunity levels (\autoref{table:coh_vac}), but included additional vaccination so that 50$\%$ of the currently na\"{\i}ve population was immunised, \autoref{table:cost50pc}. In this scenario the additional vaccination reduces the B/C ratio, and the additional vaccines for the extra immunisation mean that the cost per immunised person before the programme becomes costly reduces to \$35.74  per immunised person \label{table:cost50pc}.
